---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rstripe

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of rstripe is to interact with the [Stripe API](https://docs.stripe.com/api), from R.

It is an independent, community-developed R package for [Stripe](https://stripe.com/) (not created by or affiliated with Stripe).

## Installation

You can install the development version of rstripe like so:

``` r
pak::pak("nutrivetpet/rstripe")
```

## Getting Started

### API Key Setup

The package requires environment variables for API authentication:

- `STRIPE_API_KEY_TEST` for test mode operations
- `STRIPE_API_KEY_LIVE` for live mode operations

Set these in your `.Renviron` file with: 

```r
# pak::pak("usethis")
usethis::edit_r_environ()
```

Don't forget to restart R afterwards.

## Example

### Current API Coverage

The package currently provides limited but useful coverage of the Stripe API. You can fetch data from these Stripe resources:

```{r eval=FALSE}
library(rstripe)

# Create a client (uses STRIPE_API_KEY_TEST from your environment)
client <- rstripe("test")

# Fetch charges (payments)
charges <- list_charges(client, limit = 10)

# Fetch customers
customers <- list_customers(client, limit = 10)

# Fetch products from your catalog
products <- list_products(client, limit = 10)

# Fetch pricing information
prices <- list_prices(client, limit = 10)

# Fetch invoices
invoices <- list_invoices(client, limit = 10)

# Fetch invoice line items
invoice_items <- list_invoice_items(client, limit = 10)

# Fetch balance transactions
balance_transactions <- list_balance_transactions(client, limit = 10)

# Filter balance transactions by date range
recent_transactions <- list_balance_transactions(
  client,
  limit = 10,
  created_gte = as.Date("2025-01-01"),
  created_lte = as.Date("2025-12-31")
)

# For unlimited results, use limit = Inf
all_charges <- list_charges(client, limit = Inf)
```

All functions accept a `rstripe` client object (created with `rstripe("test")` or `rstripe("live")`), and return data as data frames (tibbles if the tibble package is installed).
